\documentclass[xcolor=svgnames,handout]{beamer}

\usepackage[utf8]    {inputenc}
%\usepackage[T1]      {fontenc}
\usepackage[english] {babel}

\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{amsmath,amsfonts,graphicx}
\usepackage{beamerleanprogress}
%\usepackage[backend=biber,style=alphabetic,sorting=ynt]{biblatex}
%\addbibresource{credits.bib}

\title
  [Careers \& FLOSS\hspace{2em}]
  {My Career \& FLOSS}

\author
  [Theodore Se\'{a}n Tubbs]
  {Theodore Se\'{a}n Tubbs}

\date
  {\today}

\institute
  {DCMO BOCES}

\setbeamertemplate{navigation symbols}{\insertframenavigationsymbol \insertsectionnavigationsymbol \insertbackfindforwardnavigationsymbol}
% navigational symbols
\begin{document}

\maketitle

\begin{frame}{High School Graduation}

After grad plans\pause

\begin{itemize}
	\item{Go on ``vacation'' and film stuff.}
	\item{Develop Typography skills:}
	\begin{itemize}
		\item{Precision.}
		\item{How to make my own stencils.}
		\item{Explore graffiti.}
		\item{Font creation}.
	\end{itemize}
	\item{Try to directly enter the workforce!}
\end{itemize}

\end{frame}

\begin{frame}{Short term Goals}
Have a:\pause
	\begin{itemize}
		\item{Fully FLOSS portfolio.}
		\item{Collection of FLOSS fonts.}
		\item{Library of FLOSS sounds, music, and stock footage.}
	\end{itemize}
Get paid based on:\pause
	\begin{itemize}
		\item{Services, not products.}
			\begin{itemize}
				\item{Editing video/audio.}
				\item{Filming.}
				\item{Taking photographs.}
				\item{Recording audio.}
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Midrange Goals}

After becoming a somewhat established artist:\pause

	\begin{itemize}
		\item{Try to encourage more sharing among artists.}
			\begin{itemize}
				\item{Make typography pieces.}
				\item{PSA videos.}
				\item{Other stuff?}
			\end{itemize}
		\item{Provide license consulting for artists and corporations.}
		\item{}
	\end{itemize}

\end{frame}

\begin{frame}{Long-range Goals}

\end{frame}

%\begin{frame}[allowframebreaks]
%\printbibliography

%\end{frame}


\end{document}

